
\section*{Conférences premier auteur}
\underline{S. Marache}, R. Prost, J. M. Rouet, et C. Lartizien, (2011). Incorporating Patient-Specific Variability in the OncoPET\_DB Database, \textit{IEEE Nuclear Science Symposium and Medical Imaging Conference}, Valence, Espagne 

\underline{S. Marache}, F. Lamare, H. Fayad, D. Visvikis, R. Prost, J. M. Rouet, and C. Lartizien, (2010), Impact of Respiratory Motion Correction on the Detection of Small Lesions in Whole-body PET Imaging: A Simulation Study, \textit{IEEE Nuclear Science Symposium and Medical Imaging Conference}, Knoxville, Tennessee, USA., pp. 3531-3533, Octobre 2010.

\section*{Articles}
C. Lartizien, \underline{S. Marache}, R. Prost (2011), Automatic Detection of Lung and Liver Lesions in 3D Positron Emission Tomography Images: a Pilot Study, \textit{IEEE Trans. on Nuclear Sciences}, sous presse.

A. Lemaitre, P. Segars, \underline{S. Marache}, A. Reilhac, M. Hatt, S. Tomei, C. Lartizien, and D. Visvikis, (2009) Incorporating patient specific variability in the simulation of realistic whole body 18F-FDG distributions for oncology applications, \textit{Proceedings of the IEEE}, vol. 97, no. 12, 2009.
Conférences

\section*{Conférences}
C. Lartizien, \underline{S. Marache}, A. Le Pogam, S. Tomei, and D. Visvikis, (2009), Impact of Partial Volume Correction in Whole-Body PET Imaging : a Computer-Aided Detection Study, \textit{Proc. of the 2009 IEEE NSS and MIC Conference}, Orlando, Floride, USA, pp. 3214-3217, Octobre 2009.

C. Lartizien, S. Tomei, and \underline{S. Marache}, (2009), Improving performance of automated detection systems for 3D PET oncology imaging by use of resampled training images, \textit{Proc. 23rd Int. CARS Conference}, Berlin, Allemagne, Springer, vol. 4, pp. (SS186-193), Juin 2009.

J. Tabary, \underline{S. Marache}, S. Valette, W. Segars, and C. Lartizien, (2009), Realistic X-Ray CT Simulation of the XCAT Phantom with SINDBAD, \textit{Proc. of the 2009 IEEE NSS and MIC Conference}, Orlando, Floride, USA, pp. 3980 - 3983, Octobre 2009.

S. Tomei, \underline{S. Marache}, C. Odet, and C. Lartizien, (2008), Automatic detection of active nodules in 3D PET oncology imaging using the Hotelling Observer and the Support Vector Machines: a comparison study, \textit{Proc of the 2008 IEEE NSS and MIC Conference}, Dresde, Allemagne, pp. 5314-5319, Octobre 2008.
